---
title: 'Positive Development community: Social network visualization'
output:
  html_document:
    df_print: paged
---

#Introduction
This document was created on 2/20/19 by Neil Yetz, MPH. The purpose of this project is to visually represent the programs in the Positive development (PD). The network graphs will assess the connections between the PD programs in the northern Colorado region. 

#Clear Environment
```{r}
rm(list=ls())
```

#Load libraries
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(igraph)
library(stringr)
library(data.table)
```


```{r, message = FALSE}
pd <- read_csv("../Data/PD System Network Mapping Survey.csv")
```

#Select & Format var names
```{r}
pd_fil <- pd %>% 
  select(4, 11:42)

#names(pd_fil) <- str_replace_all(names(pd_fil), " ", "_")


names(pd_fil) <- str_remove(names(pd_fil), "Rate the strength of each relationship that your organization has with the list of other organizations below. Leave your organization blank. ")

names(pd_fil) <- names(pd_fil) %>% str_replace_all("\\[|\\]", "")
names(pd_fil) <- names(pd_fil) %>% str_replace_all(" \\(.*\\)", "")
names(pd_fil) <- names(pd_fil) %>% str_replace_all(" \\'.*\\)", "")

names(pd_fil) <- gsub("'", '', names(pd_fil))

org_names <- names(pd_fil)


#pd_fil <- pd_fil %>% 
#  rename(`Children's Hospital Colorado: School Health & Child Health Advocacy Institute`     = "Children's Hospital Colorado: School Health & Child Health Advocacy Institute" )

#Used to create mutate shorcut excel file.
#names(pd_fil)
```


#Convert convert weights to Numeric - Weighted adjacency table
```{r}

pd_num <- pd_fil %>% 
  mutate(
          `Action for Healthy Kids` = as.numeric(readr::parse_number(`Action for Healthy Kids` )),
          `Advancing Dynamic Solutions` = as.numeric(readr::parse_number(`Advancing Dynamic Solutions` )),
          `Advancing IDEAS for Health` = as.numeric(readr::parse_number(`Advancing IDEAS for Health` )),
          `Alliance for a Healthier Generation` = as.numeric(readr::parse_number(`Alliance for a Healthier Generation` )),
          `Aurora Public Schools` = as.numeric(readr::parse_number(`Aurora Public Schools` )),
          `Center for Rural School Health and Education` = as.numeric(readr::parse_number(`Center for Rural School Health and Education`          )),
          `CharterChoice Collaborative` = as.numeric(readr::parse_number(`CharterChoice Collaborative` )),
          `Chef Ann Foundation` = as.numeric(readr::parse_number(`Chef Ann Foundation` )),
          `Children's Hospital Colorado: School Health & Child Health Advocacy Institute` = as.numeric(readr::parse_number(`Children's Hospital Colorado: School Health & Child Health Advocacy Institute`    )),
          `Colorado Alliance for School Health` = as.numeric(readr::parse_number(`Colorado Alliance for School Health` )),
          `Colorado Department of Education` = as.numeric(readr::parse_number(`Colorado Department of Education` )),
          `Colorado Department of Education: Office of School Nutrition` = as.numeric(readr::parse_number(`Colorado Department of Education: Office of School Nutrition` )),
          `Colorado Department of Human Services: Office of Behavioral Health` = as.numeric(readr::parse_number(`Colorado Department of Human Services: Office of Behavioral Health` )),
          `Colorado Department of Public Health and Environment: Children, Youth and Families Branch` = as.numeric(readr::parse_number(`Colorado Department of Public Health and Environment: Children, Youth and Families Branch`)),
          `Colorado Department of Public Safety` = as.numeric(readr::parse_number(`Colorado Department of Public Safety` )),
          `Colorado Department of Transportation` = as.numeric(readr::parse_number(`Colorado Department of Transportation` )),
          `Colorado Education Initiative` = as.numeric(readr::parse_number(`Colorado Education Initiative` )),
          `Colorado League of Charter Schools` = as.numeric(readr::parse_number(`Colorado League of Charter Schools` )),
          `Colorado PTA` = as.numeric(readr::parse_number(`Colorado PTA` )),
          `Colorado School of Public Health: Healthy Kids Colorado Survey and Smart Source team` = as.numeric(readr::parse_number(`Colorado School of Public Health: Healthy Kids Colorado Survey and Smart Source team` )),
          `Colorado State University` = as.numeric(readr::parse_number(`Colorado State University` )),
          `Fremont Regional Wellness` = as.numeric(readr::parse_number(`Fremont Regional Wellness` )),
          `Health & Innovation through Education` = as.numeric(readr::parse_number(`Health & Innovation through Education` )),
          `PlayCore` = as.numeric(readr::parse_number(`PlayCore` )),
          `Playworks` = as.numeric(readr::parse_number(`Playworks` )),
          `Resilient Futures` = as.numeric(readr::parse_number(`Resilient Futures` )),
          `RMC Health` = as.numeric(readr::parse_number(`RMC Health` )),
          `Special Olympics Colorado` = as.numeric(readr::parse_number(`Special Olympics Colorado` )),
          `Trailhead Institute` = as.numeric(readr::parse_number(`Trailhead Institute` )),
          `University of Colorado / Childrens Hospital Colorado` = as.numeric(readr::parse_number(`University of Colorado / Childrens Hospital Colorado` )),
          `University of Northern Colorado Active Schools Institute ` = as.numeric(readr::parse_number(`University of Northern Colorado Active Schools Institute ` )),
          `Wellness Training Specialists` = as.numeric(readr::parse_number(`Wellness Training Specialists` ))
)


```



#Convert top binary Adjacency table
```{r}


#Remove ID (data.table doesn't like this)
ID <- pd_num %>% 
  select(`What organization are you affiliated with?`)
pd_adj <- pd_num %>% 
  select(-`What organization are you affiliated with?`)


#Apply function to replace values greater than 0 with 1
pd_adj <- lapply(pd_adj, function(x){replace(x, x >0 ,1)})
# change to data.table
setattr(pd_adj, 'class', c('data.table','data.frame'))

#Convert back to tible (data_frame)
pd_adj <- dplyr::as_tibble(pd_adj)

pd_adj <- lapply(pd_adj, function(x){replace(x, is.na(x) ,1)})
# change to data.table
setattr(pd_adj, 'class', c('data.table','data.frame'))

#Convert back to tible (data_frame)
pd_adj <- dplyr::as_tibble(pd_adj)

#Bind the ID column back
pd_adj  <- bind_cols(ID, pd_adj)


```

#Graph adjacency table (Need to format)
Considering using [Kumu](https://kumu.io/) 
```{r}






long_DF <-pd_adj %>% gather(org, connect, `Action for Healthy Kids`:`Wellness Training Specialists` )

edge <- long_DF %>% 
  filter(connect == 1) %>% 
  select(from = "What organization are you affiliated with?" , to = "org" ) %>% 
  filter(from != to)

g <- graph_from_edgelist(as.matrix(edge), directed = TRUE)


plot(g)

#install.packages("threejs")
library(threejs)

g <- set_vertex_attr(g, "color", value = "dodgerblue")
plot(g,
     vertex.label.color = "black", 
     edge.color = 'gray77',
     vertex.size = 5,
     edge.arrow.size = 1,
      vertex.label = NA,
     layout = layout_in_circle(g)
     )


```




```{r}


#nodes <- long_DF %>% 
 # select(id = "org")

#nodes <- subset(nodes, !duplicated(id))


edges <- data.frame(from = edge$from,
                    to = edge$to)


to   <- dplyr::as_data_frame(edge$to)
from <- dplyr::as_data_frame(edge$from)

to   <- subset(to, !duplicated(value))
from <- subset(from, !duplicated(value))

to <- to %>% 
  left_join(from, by = "value")


nodes <- edges %>% 
  select(id = "from")




isolates <- from %>%
  semi_join(to, by = "value")

edges_test <- edges %>% 
  semi_join(isolates, by = c("to" = "value")) %>% 
  semi_join(isolates, by = c("from" = "value"))


nodes <- subset(nodes, !duplicated(id))

nodes_test <- nodes %>%
  semi_join(isolates, by = c("id" = "value"))

library(visNetwork)

visNetwork(nodes_test, edges_test, height = "1000px") %>%
  visIgraphLayout() %>%
  visNodes(size = 10)

visNetwork(nodes_test, edges_test) %>%
  visIgraphLayout() %>%
  visNodes(size = 10) %>%
  visOptions(highlightNearest = list(enabled = T, hover = T), 
             nodesIdSelection = T)

#layout = "layout_in_circle"
```


#Edelist to adjacency
```{r}


adjacency_table <- as.matrix(get.adjacency(graph.data.frame(edges)))



#adjacency_table2 <- adjacency_table %>% 
#    as.data.frame() %>% 
#    rownames_to_column() %>% 
#  select(org_name = "rowname",
#         everything(),
#         -`Alliance for a Healthier Generation`,
#         -`Colorado Department of Human Services: Office of Behavioral Health`,
#         -`Colorado Department of Public Safety`,
#         -`Colorado Department of Transportation`) %>% 
#  filter(org_name != "Alliance for a Healthier Generation",
#         org_name != "Colorado Department of Human Services: Office of Behavioral Health",
#         org_name != "Colorado Department of Public Safety",
#         org_name != "Colorado Department of Transportation") %>% 
#  as.matrix()
  
    
  


ad_g <- graph_from_adjacency_matrix(adjacency_table, mode = "directed")

V(ad_g)$label.cex = 1
V(ad_g)$label.cex[1:20 %% 2 == 0] = 0.

#Vad(ad_g)$size

deg=list(degree(ad_g, mode="all"))


visIgraph(ad_g,  physics = TRUE, smooth = TRUE) %>%
  visIgraphLayout() %>%
  visNodes(size = 20) %>%
  visOptions(highlightNearest = list(enabled = T, hover = T), 
             nodesIdSelection = T) 








```


#Prepare network for kumu (Weighted)
```{r}

#Convert NAs to 0
pd_num[is.na(pd_num)] <- 0

#Change forst var name
pd_num <- pd_num %>% 
  select(org = "What organization are you affiliated with?", everything())



```

```{r}
library(tidyr)
long <- pd_num %>% gather(To, Strength, `Action for Healthy Kids`:`Wellness Training Specialists`)
```



#change names
```{r}

long <- long %>% 
  filter(Strength != 0,
         org != To) %>% 
  mutate(Type = "organization") %>%  #,
   #      Strength = ifelse(Strength == 0, "No Connection", Strength),
    #     Strength = ifelse(Strength == 1, "On my radar; I know of this organization, but rarely communicate or cross paths with them.", Strength),
     #    Strength = ifelse(Strength == 2, "In my peripheral network; My organization keeps in touch with this organization and/or occasionally work, collaborate, or socialize with them.", Strength),
      #   Strength = ifelse(Strength == 3, "In my core network. My organization knows this organization well and/or frequently work, collaborate, or socialize with them.", Strength)) %>% 
  select(From = "org", To, Type, Strength) %>% 
  mutate(From = ifelse(From == "Other", "New America School", From),
         From = ifelse(From == "University of Northern Colorado Active Schools Lab", "University of Northern Colorado Active Schools Institute", From),
         From = ifelse(From == "Trailhead Insitute", "Trailhead Institute", From)
         ) %>% 
  filter(From != To,
         From != "Alliance for a Healthier Generation",
         From != "Colorado Department of Human Services: Office of Behavioral Health",
         From != "Colorado Department of Public Safety",
         From != "Colorado Department of Transportation",
         From != "Fremont Regional Wellness",
         From != "Advancing Dynamic Solutions",
         To != "Alliance for a Healthier Generation",
         To != "Colorado Department of Human Services: Office of Behavioral Health",
         To != "Colorado Department of Public Safety",
         To != "Colorado Department of Transportation",
         To != "Fremont Regional Wellness",
         To != "Advancing Dynamic Solutions",
         To != "University of Colorado / Childrens Hospital Colorado"
)




```

```{r}
write_csv(long, "kumu_final.csv") 
```


```{r}
long %>% 
  group_by(From) %>% 
  slice(1) 

long %>% 
  group_by(To) %>% 
  slice(1) 
```


#Create 6 month edgelist
```{r, warning = FALSE}
six_mo <- pd %>% 
  select(org = "What organization are you affiliated with?", six_mo = "Who has your organization shared resources with and/or increased peer learning with in the last 6 months? Check all that apply. Peer learning here refers to sharing of knowledge, ideas, and experiences between organizations (Boud, 1988).") %>% 
  separate(six_mo, sep = ";", into = c("a","b", "c","d", "e", "f", "g", "i", "j", "k", "l", "m", "n", "o", "p", "q", "r", "s", "t", "u", "v", "w", "x", "y", "z")) %>% 
  gather(from, to, a:z) %>% 
  filter(!is.na(to)) %>% 
  select(-from) %>% 
  select(from = "org", to) %>% 
  mutate(from  = ifelse(from == "Other", "New America School", from),
          from = ifelse(from == "University of Northern Colorado Active Schools Lab", "University of Northern Colorado Active Schools Institute", from),
          from = ifelse(from == "Trailhead Insitute", "Trailhead Institute", from) ,
          to   = ifelse(to   == "University of Northern Colorado Active Schools Lab", "University of Northern Colorado Active Schools Institute", to),
          to   = ifelse(to   == "Trailhead Insitute", "Trailhead Institute", to) 
         ) %>% 
  filter(from != to,
         from != "Alliance for a Healthier Generation",
         from != "Colorado Department of Human Services: Office of Behavioral Health",
         from != "Colorado Department of Public Safety",
         from != "Colorado Department of Transportation",
         from != "Fremont Regional Wellness",
         from != "Advancing Dynamic Solutions",
         from != "Advancing Dynamic (AD) Solutions",
         from != "University of Colorado / Children's Hospital Colorado",
         to   != "Alliance for a Healthier Generation",
         to   != "Colorado Department of Human Services: Office of Behavioral Health",
         to   != "Colorado Department of Public Safety",
         to   != "Colorado Department of Transportation",
         to   != "Fremont Regional Wellness",
         to   != "Advancing Dynamic Solutions",
         to   != "University of Colorado / Childrens Hospital Colorado",
         to   != "Advancing Dynamic (AD) Solutions",
         to   != "University of Colorado / Children's Hospital Colorado"
         )

write_csv(six_mo, "six_mo.csv")
```

#Graph six month edgelist
```{r}

six_nodes <- six_mo %>%
  select(from = "to") %>% 
  group_by(from) %>% 
  slice(1) %>% 
  ungroup()

six_to <- six_mo %>% 
  select(to, from)

six_test <- six_to %>% 
  select(from) %>% 
  group_by(from) %>% 
  slice(1) %>%
  ungroup() %>% 
  anti_join(six_nodes, by = "from") %>% 
  mutate(to = "Other")

six_to <- bind_rows(six_to, six_test)

g <- graph_from_edgelist(as.matrix(six_to))

export <- dplyr::as_data_frame(as_edgelist(g))

export <- export %>%
  select(From = "V1", To = "V2")

write_csv(export, "six_mo.csv")

```





